Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-01-13 grove-paper.tex
add note on theorem placement
update grammar and arity table

% constructors
\def\ExpVar{\mathsf{Exp\_var}}
\def\ExpLam{\mathsf{Exp\_lam}}
\def\ExpApp{\mathsf{Exp\_app}}
\def\ExpNum{\mathsf{Exp\_num}}
\def\ExpPlus{\mathsf{Exp\_plus}}
\def\PatVar{\mathsf{Pat\_var}}
\def\TypNum{\mathsf{Typ\_num}}
\def\TypArrow{\mathsf{Typ\_arrow}}

@@

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{lrlll}
      \textrm{Operators:}         & op   & {}\in Ops & {}::={} & + \mid \ast{} \\
      \textrm{Patterns:}          & q    & {}\in Pat & {}::={} & x \mid \hole \mid \{q|\ldots|q\} \\
      \textrm{Expressions:\qquad} & e    & {}\in Exp & {}::={} & x \mid \lambda q \mathord{:}\tau.e \mid e~e \mid e~op~e \mid n \\
                                  &      &           &         & \phantom{x} \mid \hole \mid \{e|\ldots|e\} \\
      \textrm{Types:}             & \tau & {}\in Typ & {}::={} & \tau \rightarrow \tau \mid Num \mid \hole \mid \{ \tau | \ldots | \tau \} \\
    \end{array}
  \]
  \caption{Syntax as a grammar for the lambda calculus that we are considering.}
  % TODO add references into multiparent store and cycles store
  \label{fig:Syntax as a grammar}
\end{figure}

@@

The language we are modeling is shown in \autoref{fig:Syntax as a grammar},
standard for a simply-typed lambda calculus except that all types of terms have
unfilled holes (represented by $\hole$), and most types of terms have conflict holes (of the form $\{\cdot | \ldots | \cdot\}$). In particular, the argument to a lambda can be either a bound variable or a hole.

@@

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{ll}
      \arity : \K \hfil \rightarrow & \wp(\P)                                        \\
      \hline
      \arity(k_0)={}        & \left\{ \Root \right\}                         \\
      \arity(x \in Pat)={}      & \left\{ \right\}                               \\
      \arity(x \in Exp)={}      & \left\{ \right\}                               \\
      \arity(\lambda q \mathord{:}\tau.e)={}      & \left\{ \mathtt{Param}, \mathtt{Type}, \mathtt{Body} \right\} \\
      \arity(e~e)={}      & \left\{ \mathtt{Fun}, \mathtt{Arg} \right\}              \\
      \arity(e~op~e)={}     & \left\{ \mathtt{L}, \mathtt{R} \right\}         \\
      \arity(n)={}      & \left\{ \right\}                               \\
      \arity(\tau \rightarrow \tau)={}    & \left\{ \mathtt{Arg}, \mathtt{Result} \right\}       \\
      \arity(Num)={}      & \left\{ \right\}                               \\
    \end{array}
  \]
  \caption{Constructors, Indexes and Arity}
  \label{fig:Constructors, Indexes and Arity}
\end{figure}

@@

>>>>

% constructors
\def\ExpVar{\mathsf{Exp\_var}}
\def\ExpLam{\mathsf{Exp\_lam}}
\def\ExpApp{\mathsf{Exp\_app}}
\def\ExpNum{\mathsf{Exp\_num}}
\def\ExpPlus{\mathsf{Exp\_plus}}
\def\ExpTimes{\mathsf{Exp\_times}}
\def\PatVar{\mathsf{Pat\_var}}
\def\TypNum{\mathsf{Typ\_num}}
\def\TypArrow{\mathsf{Typ\_arrow}}

@@

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{lrlll}
      \textrm{Patterns:}          & q    & {}\in Pat & {}::={} & x^u \mid \hole \mid \{q | \ldots | q\} \\
      \textrm{Types:}             & \tau & {}\in Typ & {}::={} & \tau \rightarrow^u \tau \mid Num^u \mid \hole \mid \{ \tau | \ldots | \tau \} \\
      \textrm{Expressions:\qquad} & e    & {}\in Exp & {}::={} & x^u \mid \lambda^u q \mathord{:}\tau.e \mid (e~e)^u \mid n^u \\
                                  &      &           &         & ~\mid e~\texttt{+}^u~e \mid e~\texttt{*}^u~e \mid \hole \mid \{e|\ldots|e\} \\
    \end{array}
  \]
  \caption{Syntax as a grammar for the lambda calculus that we are considering.}
  % TODO add references into multiparent store and cycles store
  \label{fig:Syntax as a grammar}
\end{figure}

@@

The language we are modeling is shown in \autoref{fig:Syntax as a grammar},
standard for a simply-typed lambda calculus except that all sorts have empty
holes (represented by $\hole$) and conflict holes (of the form $\{q | \ldots |
q\}$). In particular, the argument to a lambda can be either a bound variable or
a hole. All constructors carry a superscripted identifier $u \in \U$.

@@

\begin{figure}
  \[
    \arraycolsep=0pt
    \begin{array}{ll}
      \arity : \K \hfil \rightarrow & \wp(\P)                                        \\
      \hline
      \arity(\Root)={}        & \left\{ \Root \right\}                         \\
      \arity(\PatVar)={}      & \left\{ \right\}                               \\
      \arity(\ExpVar)={}      & \left\{ \right\}                               \\
      \arity(\ExpLam)={}      & \left\{ \mathtt{Param}, \mathtt{Type}, \mathtt{Body} \right\} \\
      \arity(\ExpApp)={}      & \left\{ \mathtt{Fun}, \mathtt{Arg} \right\}              \\
      \arity(\ExpPlus)={}     & \left\{ \mathtt{L}, \mathtt{R} \right\}         \\
      \arity(\ExpTimes)={}    & \left\{ \mathtt{L}, \mathtt{R} \right\}         \\
      \arity(\ExpNum)={}      & \left\{ \right\}                               \\
      \arity(\TypArrow)={}    & \left\{ \mathtt{Arg}, \mathtt{Result} \right\}       \\
      \arity(\TypNum)={}      & \left\{ \right\}                               \\
    \end{array}
  \]
  \caption{Constructors, Indexes and Arity}
  \label{fig:Constructors, Indexes and Arity}
\end{figure}

@@

Theorem: well-sorted graphs produce decompositions of well-sorted trees
